The \project{unRAVE} catalog

### 2016-08-18 article/unrave.tex
Add paragraph stem about rave dr4/5 comparisons

% External validation: 
% --> RAVE Data Release 4
% --> Gaia-ESO Survey
% --> APOGEE / EPIC (whichever was not used)
% --> Literature studies presented in Kordopatis+ 2014
% --> Gold standards (incl. exoplanet host star studies): Reddy (2003, 2006), Bensby (2014), Valenti & Fischer (2005)

@@

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundance labels we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Da_Costa,Carretta_2009}.  In the \rave\
survey we found 70 stars with positions and radial velocities that are
consistent with being members of globular clusters.  Specifically we identified
49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde
globular cluster NGC~3201, and 10 members of NGC~362.  
% TODO: Were any of these stars unintentionally in the training set?
All of these systems are well-studied and exhibit abundance anti-correlations 
in Na--O and Mg--Al \citep{people}.  Other correlations are also present 
(e.g., C--N), but those relationships are less relevant for this work because 
we do not measure C and N abundances here.

@@

\begin{figure*}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release.\label{fig:rave-dr4-comparison}}
\end{figure*}

@@

\begin{figure*}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{Kordopatis_2013}}
\end{figure*}

>>>>

Here we cross-match our results against literature samples to verify that
our labels are accurate.  Because this work is an independent analysis, our
first point of reference is against the official \rave\ data releases.  These
comparisons are shown in Figures \ref{fig:rave-dr4-comparison} and 
\ref{fig:rave-dr5-comparison}, where we show our labels with respect to the
results in the fourth and fifth \rave\ data releases, respectively.  In order
to provide a fair comparison we only show stars that meet a number of quality
flags in both samples. 
\stub{What selections qualify as a fair comparison in both samples?}
There is very good agreement in $\teff$, with a bias
and RMS of just XX~K and XXX~K, respectively.  We find our $\logg$ values are
closest to the `calibrated' \rave\ surface gravities, which make use of 
asteroseismic information to correct (increase) the $\logg$ values along the
giant branch.  The calibrated \rave\ surface gravities also correct the 
location of the red clump (by $\sim0.5$~dex) to be in the same position in our
results.  However, while our $\logg$ values generally agree with the calibrated
\rave\ values along the giant branch, our $\logg$ values do differ slightly 
along the main-sequence.  This is principally because the main-sequence in 
this work tends to taper down towards higher $\logg$ values at cooler 
temperatures, whereas the comparison sample tend to have a slightly flatter
main-sequence.  This difference is not likely to have a very significant 
effect on the detailed abundance or spectrophotometric distance determinations
between these studies.

\stub{What abundances are available?}
\stub{Any differences in RAVE abundances?}

% External validation: 
% --> Gaia-ESO Survey
% --> APOGEE / EPIC (whichever was not used)
% --> Literature studies presented in Kordopatis+ 2014
% --> Gold standards (incl. exoplanet host star studies): Reddy (2003, 2006), Bensby (2014), Valenti & Fischer (2005)

@@

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundance labels we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Da_Costa,Carretta_2009}.  In the \rave\
survey we found 70 stars with positions and radial velocities that are
consistent with being members of globular clusters.  Specifically we identified
49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde
globular cluster NGC~3201, and 10 members of NGC~362.  
\stub{Were any of these stars unintentionally in the training set?}
All of these systems are well-studied and exhibit abundance anti-correlations 
in Na--O and Mg--Al \citep{people}.  Other correlations are also present 
(e.g., C--N), but those relationships are less relevant for this work because 
we do not measure C and N abundances here.

@@

\begin{figure*}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release \citep{Kordopatis_2014}.\label{fig:rave-dr4-comparison}}
\end{figure*}

\begin{figure*}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fifth data release \citep{Kunder_2016}.\label{fig:rave-dr5-comparison}}
\end{figure*}

@@

\begin{figure*}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{Kordopatis_2014}}
\end{figure*}
